### 2017-10-13 Gruba/01-intro.tex

Our paper is organized as follows.
Section \ref{sec:overv} gives the problem formulation and system overviews, followed by detailed explanations in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm} separately.
Section \ref{sec:perf} provides the performance evaluation.
Related work is presented in Section \ref{sec:rela}.
Finally, Section \ref{sec:conclu} concludes the work.

>>>>

Our paper is organized as follows.
Section \ref{sec:overv} gives the problem formulation and system overview, followed by detailed explanations in Sections \ref{sec:fe}, \ref{sec:uc} and \ref{sec:gm}.
Section \ref{sec:perf} provides the performance evaluation.
Related work is presented in Section \ref{sec:rela}.
Finally, Section \ref{sec:conclu} concludes the work.
